Global Climate and Atmospheric Composition of the Ultra-Hot Jupiter WASP-103\lowercase{b} from \HST\ and \Spitzer\ Phase Curve Observations

### 2018-02-08 ms.tex
table

\begin{deluxetable}{llllllll}
	\tablecolumns{8}
	\tablewidth{0pt}
	\tablecaption{Model Comparison \label{table:models}}
	\tablehead{
	\colhead{Data} & \colhead{Model} & \colhead{$T_\mathrm{min}$} & \colhead{$T_\mathrm{max}$} & \colhead{$\overline{T}_\mathrm{night}$} & \colhead{$\overline{T}_\mathrm{day}$} &\colhead{$\Delta_\mathrm{AIC}$} & \colhead{$\Delta_\mathrm{BIC}$}}
		\startdata
		WFC3 & Sph. Harmonics & 1214 & 3251 & 1820 & 2622 & 0.0 & 0.0 \\
		\, & Kinematic & 1980 & 3958 & 1980 & 2777 & 14.0 & 14.0 \\
		\, & Two Temp. & 0 & 2887 & 0 & 2887 & 49.8 & 45.4 \\
		\, & Sinusoid & -- & -- & -- & -- & 19.8 & 15.4 \\
		Ch 1 & Sph. Harmonics & 1280 & 3444 & 1936 & 2786 & 49.0 & 0.0 \\
		\, & Kinematic & 1955 & 3675 & 1999 & 2656 & 83.3 & 34.3 \\
		\, & Two Temp. & 1429 & 3041 & 1429 & 3025 & 59.7 & 17.6 \\
		\, & Sinusoid & -- & -- & -- & -- & 0.0 & 76.6 \\
		Ch 2 & Sph. Harmonics & 902 & 3786 & 1753 & 2920 & 7.9 & 2.3 \\
		\, & Kinematic & 1703 & 4276 & 1711 & 2740 & 20.8 & 15.2 \\
		\, & Two Temp. & 1361 & 3311 & 1361 & 3292 & 12.5 & 0.0 \\
		\, & Sinusoid & -- & -- & -- & -- & 0.0 & 22.3 \\
		\enddata
		\vspace{-0.8cm}
		\tablecomments{comments}
	\end{deluxetable}

@@

\begin{figure}
\includegraphics[width = 0.5\textwidth]{Figures/w103b_transmission_spectrum.pdf}
\caption{The transmission spectrum of WASP-103b (points) for a range of assumptions about the planet's nightside temperature. The gray points correspond to no correction for the nightside flux. The blue and red points are the corrected for an average nightside photospheric temperature is 1400 and 2000 K, respectively. The atmospheric scale height is $5.5\times10^6$ m, assuming a mean molecular weight of 2.3 amu, surface gravity $g = 15.85 m/s^2$, and a temperature $T = 2410$ K.}
\label{fig:tspec}
\end{figure}

>>>>

\begin{deluxetable}{llllllll}
	\tablecolumns{8}
	\tablewidth{0pt}
	\tablecaption{Model Comparison \label{table:models}}
	\tablehead{
	\colhead{Data} & \colhead{Model} & \colhead{$T_\mathrm{min}$} & \colhead{$T_\mathrm{max}$} & \colhead{$\overline{T}_\mathrm{night}$} & \colhead{$\overline{T}_\mathrm{day}$} &\colhead{$\Delta_\mathrm{AIC}$} & \colhead{$\Delta_\mathrm{BIC}$}}
	\startdata
	WFC3 & Sph. Harmonics & 1227 & 3237 & 1822 & 2636 & 0.0 & 0.0 \\
	\, & Kinematic & 1977 & 3953 & 1977 & 2769 & 14.1 & 14.1 \\
	\, & Two Temp. & 0 & 2879 & 0 & 2879 & 46.3 & 41.9 \\
	\, & Sinusoid & -- & -- & -- & -- & 21.0 & 16.5 \\
	Ch 1 & Sph. Harmonics & 1269 & 3391 & 1912 & 2741 & 0.0 & 49.0 \\
	\, & Kinematic & 1932 & 3630 & 1975 & 2614 & 34.2 & 83.4 \\
	\, & Two Temp. & 1418 & 2990 & 1418 & 2990 & 17.6 & 59.7 \\
	\, & Sinusoid & -- & -- & -- & -- & 76.6 & 0.0 \\
	Ch 2 & Sph. Harmonics & 888 & 3714 & 1729 & 2864 & 7.9 & 2.3 \\
	\, & Kinematic & 1614 & 3931 & 1621 & 2544 & 20.8 & 15.2 \\
	\, & Two Temp. & 1344 & 3241 & 1344 & 3241 & 12.5 & 0.0 \\
	\, & Sinusoid & -- & -- & -- & -- & 0.0 & 22.3 \\
	\enddata
	\vspace{-0.8cm}
	\tablecomments{comments}
\end{deluxetable}

@@

\begin{figure}
\includegraphics[width = 0.5\textwidth]{Figures/w103b_transmission_spectrum.pdf}
\caption{The transmission spectrum of WASP-103b (points) for a range of assumptions about the planet's nightside temperature. The gray points are not corrected for planet nightside flux, whereas the blue and red points are corrected for an average nightside photospheric temperature of 1400 and 2000 K, respectively. The dotted line corresponds to the mean transit depth (assuming $T_\mathrm{night} = 2000$ K). Atmospheric scale height $H$ is shown on the right y-axis, where $H = 5.5\times10^6$ m (assuming a mean molecular weight of 2.3 atomic mass units, surface gravity $g = 15.85$ m/s$^2$, and a temperature $T = 2410$ K).}
\label{fig:tspec}
\end{figure}
